---
title: "Module_12"
author: "Gisela Gonzalez"
date: "March 30th 2021"
output: word_document
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown Practice 

Hello, this is my *first experience with R markdown*.  If you're interested in learning more about R Markdown, please check out [link](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf).

## Summary Data of mtcars data generate in R
```{r data(mtcars)}
summary(mtcars)
```

### Plot mtcars data

Now that we have our data, it's time to try to create a **bar graph**!The bar graph will show the number of gear type in mtcars.
```{r}
geartype <- table(mtcars$gear)
xval <- c("Type3", "type 4", "type 5")
barplot(geartype, names.arg=xval, xlab="Gear Types", ylab="Total number of each type", col="red", main = "Distribution of Gear Types")
```

#### Conclusion 

Thanks for joining me on experimenting with R markdown. I've learned that:
* R Markdown is a format used for writing reproducible, dynamic reports in R.
* It is simple and fun to use. 

